\Title

### 2016-08-17 manuscript/manuscript.tex
Mention that Bouguer plate works
Fixes #28

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
\citep{silva2014} to use tesseroids as model elements and Tikhonov
regularization.
The computational efficiency of our method is due to
using Bott's approximation for the Jacobian matrix
(Eq.~\ref{eq:bott-gaussnewton})
and using sparse matrix algorithms for arithmetic operations and the solution
of linear systems..
We employ two cross-validation techniques to estimate the hyper-parameters of
the inversion: the regularization parameter, the Moho density-contrast, and the
Normal Earth Moho depth.

>>>>

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
\citep{silva2014} to use tesseroids as model elements and Tikhonov
regularization.
The computational efficiency of our method is due to
using Bott's approximation for the Jacobian matrix
(Eq.~\ref{eq:bott-gaussnewton})
and using sparse matrix algorithms for arithmetic operations and the solution
of linear systems.
The Bouguer plate approximation in Eq.~\ref{eq:bott-gaussnewton} is adequate
and the method converges
even when the data are at higher altitudes and the model is not outcropping,
as shown by the applications to synthetic data.
We employ two cross-validation techniques to estimate the hyper-parameters of
the inversion: the regularization parameter, the Moho density-contrast, and the
Normal Earth Moho depth.
